---
title: "P8106 Data Science II – Midterm Project"
author: "Group 33: Zichen Fan, Yiming Cao"
date: "2026-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  message   = FALSE,
  warning   = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 5
)
set.seed(2026)
```

```{r packages}
library(tidyverse)
library(caret)
library(glmnet)
library(corrplot)
library(ggpubr)
library(knitr)
library(kableExtra)
library(car)
library(lmtest)
```

---

# Part I — Building a Prediction Model for Researcher A (1990–1995 Cohort)

## Data Loading and Preprocessing

```{r load-data}
load("data/datA.RData")
load("data/datB.RData")

dat_a <- datA
dat_b <- datB
```

Numerically coded categorical variables are converted to factors with descriptive labels.

```{r factor-coding}
recode_factors <- function(df) {
  df |> mutate(
    menopause = factor(menopause, levels = 0:1,
                       labels = c("Pre", "Post")),
    race = factor(race, levels = 1:4,
                  labels = c("White", "Black", "Asian", "Hispanic")),
    tumor_grade = factor(tumor_grade, levels = 1:3,
                         labels = c("Well", "Moderate", "Poor")),
    ER = factor(ER, levels = 0:1, labels = c("Neg", "Pos")),
    PR = factor(PR, levels = 0:1, labels = c("Neg", "Pos")),
    HER2 = factor(HER2, levels = 0:1, labels = c("Neg", "Pos")),
    stage = factor(stage, levels = 1:3, labels = c("I", "II", "III")),
    surgery = factor(surgery, levels = 0:1,
                     labels = c("BCS", "Mastectomy")),
    chemo = factor(chemo, levels = 0:1, labels = c("No", "Yes")),
    hormonal_therapy = factor(hormonal_therapy, levels = 0:1,
                              labels = c("No", "Yes"))
  )
}

dat_a <- recode_factors(dat_a)
dat_b <- recode_factors(dat_b)

x_a <- dat_a |> select(-id, -log_PFS)
y_a <- dat_a$log_PFS
x_b <- dat_b |> select(-id, -log_PFS)
y_b <- dat_b$log_PFS

cat("datA: n =", nrow(dat_a), " | predictors =", ncol(x_a), "\n")
cat("datB: n =", nrow(dat_b), " | predictors =", ncol(x_b), "\n")
```

## Missing Data

```{r missing-data}
missing_tbl <- dat_a |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") |>
  filter(n_missing > 0)

if (nrow(missing_tbl) == 0) {
  cat("No missing values detected in datA.\n")
} else {
  kable(missing_tbl, caption = "Missing values in datA") |>
    kable_styling(full_width = FALSE)
}
```

## Exploratory Data Analysis

### Outcome: log(PFS)

```{r eda-outcome, fig.cap="Distribution and normality check of log(PFS) in datA"}
p_hist <- ggplot(dat_a, aes(x = log_PFS)) +
  geom_histogram(bins = 40, fill = "steelblue", color = "white", alpha = 0.85) +
  labs(title = "Histogram of log(PFS)",
       x = "log(PFS) in months", y = "Count") +
  theme_bw()

p_qq <- ggplot(dat_a, aes(sample = log_PFS)) +
  stat_qq(color = "steelblue", alpha = 0.5) +
  stat_qq_line(color = "firebrick") +
  labs(title = "Normal Q-Q Plot") +
  theme_bw()

ggarrange(p_hist, p_qq, ncol = 2)
ggsave("figures/eda_1_outcome_dist.png", width = 12, height = 5, dpi = 300)
```

### Continuous Predictors

```{r eda-continuous, fig.height=7, fig.cap="Continuous predictors vs. log(PFS) with loess smoother"}
cont_vars <- c("age", "bmi", "tumor_size", "lymph_nodes", "Ki67")

dat_a |>
  select(all_of(cont_vars), log_PFS) |>
  pivot_longer(-log_PFS, names_to = "variable", values_to = "value") |>
  ggplot(aes(x = value, y = log_PFS)) +
  geom_point(alpha = 0.25, size = 0.7, color = "steelblue") +
  geom_smooth(method = "loess", se = TRUE,
              color = "firebrick", linewidth = 0.8) +
  facet_wrap(~ variable, scales = "free_x", ncol = 3) +
  labs(title = "Continuous Predictors vs. log(PFS)",
       x = "Predictor value", y = "log(PFS)") +
  theme_bw()
ggsave("figures/eda_continuous_loess.png", width = 12, height = 8, dpi = 300)
```

### Categorical Predictors

```{r eda-categorical, fig.height=9, fig.cap="log(PFS) distribution by categorical predictors"}
cat_vars <- c("menopause", "race", "tumor_grade",
              "ER", "PR", "HER2", "stage",
              "surgery", "chemo", "hormonal_therapy")

dat_a |>
  select(all_of(cat_vars), log_PFS) |>
  pivot_longer(-log_PFS, names_to = "variable", values_to = "level") |>
  ggplot(aes(x = level, y = log_PFS, fill = level)) +
  geom_boxplot(alpha = 0.7, outlier.size = 0.4) +
  facet_wrap(~ variable, scales = "free_x", ncol = 4) +
  labs(title = "log(PFS) by Categorical Predictors",
       x = NULL, y = "log(PFS)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1, size = 7))
ggsave("figures/eda_categorical_boxplot.png", width = 12, height = 9, dpi = 300)
```

### Correlation Matrix

```{r eda-correlation, fig.width=8, fig.height=8, fig.cap="Correlation matrix of all variables"}
numeric_for_cor <- datA |> select(-id)
cor_mat <- cor(numeric_for_cor)

corrplot(cor_mat, method = "color", type = "lower",
         tl.cex = 0.75, tl.col = "black",
         addCoef.col = "black", number.cex = 0.55,
         diag = FALSE,
         title = "Pearson Correlation – All Variables")
```

```{r save-corr, include=FALSE}
png("figures/eda_correlation_matrix.png", width = 1000, height = 1000, res = 150)
corrplot(cor_mat, method = "color", type = "lower",
         tl.cex = 0.75, tl.col = "black",
         addCoef.col = "black", number.cex = 0.55,
         diag = FALSE,
         title = "Pearson Correlation – All Variables")
dev.off()
```

### EDA Summary

The correlation matrix reveals notable multicollinearity: ER and PR are highly correlated (r = 0.74), ER and hormonal therapy are correlated (r = 0.65), and stage shares substantial overlap with tumor size and lymph node count since staging criteria incorporate these variables. Several predictors show negligible association with log(PFS), including BMI, menopause status, and race. The loess curves for continuous predictors suggest roughly linear relationships with log(PFS).

These findings motivate the use of elastic net regression, which simultaneously performs variable selection and handles correlated predictors through its combined L1/L2 penalty. This is preferable to ordinary least squares here because OLS coefficient estimates can become unstable and inflated when predictors are correlated.

## Model Training

We use elastic net with `caret` to tune both the mixing parameter alpha (0 = ridge, 1 = lasso) and the regularization strength lambda via 10-fold cross-validation.

```{r model-data}
dat_a_model <- dat_a |> select(-id)
dat_b_model <- dat_b |> select(-id)

x_mat <- model.matrix(log_PFS ~ ., data = dat_a_model)[, -1]
y_vec <- dat_a_model$log_PFS
```

```{r enet-tuning}
ctrl <- trainControl(method = "cv", number = 10)

enet_grid <- expand.grid(
  alpha = seq(0, 1, by = 0.1),
  lambda = 10^seq(-4, 0, length.out = 50)
)

enet_fit <- train(x_mat, y_vec,
                  method = "glmnet",
                  trControl = ctrl,
                  tuneGrid = enet_grid)

enet_fit$bestTune
plot(enet_fit, main = "Elastic Net: CV RMSE across alpha and lambda")
```

Fine-tune around the best alpha from the initial search.

```{r enet-finetune}
fine_grid <- expand.grid(
  alpha = seq(max(0, enet_fit$bestTune$alpha - 0.1),
              min(1, enet_fit$bestTune$alpha + 0.1), by = 0.02),
  lambda = 10^seq(log10(enet_fit$bestTune$lambda) - 1,
                  log10(enet_fit$bestTune$lambda) + 1, length.out = 50)
)

enet_fine <- train(x_mat, y_vec,
                   method = "glmnet",
                   trControl = ctrl,
                   tuneGrid = fine_grid)

best_alpha <- enet_fine$bestTune$alpha
best_lambda <- enet_fine$bestTune$lambda
cat("Best alpha:", best_alpha, "\n")
cat("Best lambda:", best_lambda, "\n")
cat("CV RMSE:", min(enet_fine$results$RMSE, na.rm = TRUE), "\n")
cat("CV R-squared:", max(enet_fine$results$Rsquared, na.rm = TRUE), "\n")
```

## Variable Selection and OLS Refit

Extract the variables selected by elastic net (nonzero coefficients), then refit with OLS to obtain standard errors, p-values, and confidence intervals.

```{r enet-coefs}
enet_coefs <- coef(enet_fine$finalModel, s = best_lambda)
enet_coefs

selected <- rownames(enet_coefs)[which(enet_coefs != 0)][-1]
cat("Selected features:\n")
print(selected)
```

```{r ols-refit}
all_predictors <- names(dat_a_model)[names(dat_a_model) != "log_PFS"]
refit_vars <- c()
for (v in all_predictors) {
  if (any(grepl(paste0("^", v), selected))) {
    refit_vars <- c(refit_vars, v)
  }
}
refit_vars <- unique(refit_vars)

refit_formula <- as.formula(
  paste("log_PFS ~", paste(refit_vars, collapse = " + "))
)
final_model_A <- lm(refit_formula, data = dat_a_model)
summary(final_model_A)
```

## Model Diagnostics

```{r diagnostics, fig.width=10, fig.height=8, fig.cap="Diagnostic plots for the final model"}
par(mfrow = c(2, 2))
plot(final_model_A)
```

```{r vif}
vif(final_model_A)
```

```{r bp-test}
bptest(final_model_A)
```

## Model Performance on Dataset A

```{r performance-A}
pred_A <- predict(final_model_A, newdata = dat_a_model)

perf_A <- data.frame(
  Metric = c("R-squared", "Adjusted R-squared", "RMSE", "MAE"),
  Training = round(c(
    summary(final_model_A)$r.squared,
    summary(final_model_A)$adj.r.squared,
    sqrt(mean((y_a - pred_A)^2)),
    mean(abs(y_a - pred_A))
  ), 4),
  CV = round(c(
    max(enet_fine$results$Rsquared, na.rm = TRUE),
    NA,
    min(enet_fine$results$RMSE, na.rm = TRUE),
    min(enet_fine$results$MAE, na.rm = TRUE)
  ), 4)
)

kable(perf_A, caption = "Table 1: Model Performance on Dataset A") |>
  kable_styling(full_width = FALSE)
```

```{r coef-table}
coef_df <- as.data.frame(summary(final_model_A)$coefficients)
coef_df$Variable <- rownames(coef_df)
coef_df <- coef_df |>
  select(Variable, everything()) |>
  mutate(CI_lower = Estimate - 1.96 * `Std. Error`,
         CI_upper = Estimate + 1.96 * `Std. Error`)

kable(coef_df, digits = 4,
      caption = "Table 2: Final Model Coefficients with 95% CI") |>
  kable_styling(full_width = FALSE)
```

---

# Part II — Generalization to Researcher B's Dataset (2000–2005 Cohort)

## Apply Model A to Dataset B

```{r predict-B}
pred_B <- predict(final_model_A, newdata = dat_b_model)

R2_B <- 1 - sum((y_b - pred_B)^2) / sum((y_b - mean(y_b))^2)
RMSE_B <- sqrt(mean((y_b - pred_B)^2))
MAE_B <- mean(abs(y_b - pred_B))

perf_compare <- data.frame(
  Metric = c("R-squared", "RMSE", "MAE"),
  DataA_Training = round(c(summary(final_model_A)$r.squared,
                           sqrt(mean((y_a - pred_A)^2)),
                           mean(abs(y_a - pred_A))), 4),
  DataB_External = round(c(R2_B, RMSE_B, MAE_B), 4)
)

kable(perf_compare,
      caption = "Table 3: Model A Performance — Dataset A vs Dataset B") |>
  kable_styling(full_width = FALSE)
```

```{r pred-vs-actual, fig.width=10, fig.height=5, fig.cap="Predicted vs actual log(PFS): Dataset A (left) and Dataset B (right)"}
p_a <- ggplot(data.frame(Actual = y_a, Predicted = pred_A),
              aes(x = Actual, y = Predicted)) +
  geom_point(alpha = 0.2, size = 0.8, color = "steelblue") +
  geom_abline(slope = 1, intercept = 0, color = "firebrick", linetype = "dashed") +
  labs(title = "Dataset A", x = "Actual log(PFS)", y = "Predicted log(PFS)") +
  theme_bw()

p_b <- ggplot(data.frame(Actual = y_b, Predicted = pred_B),
              aes(x = Actual, y = Predicted)) +
  geom_point(alpha = 0.2, size = 0.8, color = "steelblue") +
  geom_abline(slope = 1, intercept = 0, color = "firebrick", linetype = "dashed") +
  labs(title = "Dataset B", x = "Actual log(PFS)", y = "Predicted log(PFS)") +
  theme_bw()

ggarrange(p_a, p_b, ncol = 2)
ggsave("figures/pred_vs_actual.png", width = 12, height = 5, dpi = 300)
```

```{r residual-B, fig.width=10, fig.height=5, fig.cap="Residual distributions when Model A is applied to both datasets"}
resid_df <- bind_rows(
  data.frame(Residual = y_a - pred_A, Dataset = "A"),
  data.frame(Residual = y_b - pred_B, Dataset = "B")
)

ggplot(resid_df, aes(x = Residual, fill = Dataset)) +
  geom_histogram(bins = 40, alpha = 0.6, position = "identity", color = "white") +
  labs(title = "Residual Distribution: Model A on Dataset A vs B",
       x = "Residual (Actual - Predicted)", y = "Count") +
  theme_bw()
ggsave("figures/residual_comparison.png", width = 10, height = 5, dpi = 300)
```

```{r bias-check}
cat("Mean residual on Dataset A:", round(mean(y_a - pred_A), 4), "\n")
cat("Mean residual on Dataset B:", round(mean(y_b - pred_B), 4), "\n")
```

## Cohort Comparison

```{r cohort-comparison}
summary_a <- datA |>
  select(-id) |>
  summarise(across(everything(), list(mean = mean, sd = sd))) |>
  pivot_longer(everything(),
               names_to = c("variable", "stat"),
               names_pattern = "(.+)_(mean|sd)") |>
  pivot_wider(names_from = stat, values_from = value) |>
  mutate(cohort = "A (1990-1995)")

summary_b <- datB |>
  select(-id) |>
  summarise(across(everything(), list(mean = mean, sd = sd))) |>
  pivot_longer(everything(),
               names_to = c("variable", "stat"),
               names_pattern = "(.+)_(mean|sd)") |>
  pivot_wider(names_from = stat, values_from = value) |>
  mutate(cohort = "B (2000-2005)")

cohort_tbl <- bind_rows(summary_a, summary_b) |>
  pivot_wider(names_from = cohort,
              values_from = c(mean, sd),
              names_glue = "{cohort}_{.value}") |>
  select(variable, starts_with("A"), starts_with("B"))

kable(cohort_tbl, digits = 3,
      caption = "Table 4: Covariate Comparison Between Cohorts") |>
  kable_styling(full_width = FALSE)
```

## Rebuild Model on Dataset B

```{r enet-B}
x_mat_B <- model.matrix(log_PFS ~ ., data = dat_b_model)[, -1]
y_vec_B <- dat_b_model$log_PFS

enet_grid_B <- expand.grid(
  alpha = seq(0, 1, by = 0.1),
  lambda = 10^seq(-4, 0, length.out = 50)
)

enet_fit_B <- train(x_mat_B, y_vec_B,
                    method = "glmnet",
                    trControl = ctrl,
                    tuneGrid = enet_grid_B)

fine_grid_B <- expand.grid(
  alpha = seq(max(0, enet_fit_B$bestTune$alpha - 0.1),
              min(1, enet_fit_B$bestTune$alpha + 0.1), by = 0.02),
  lambda = 10^seq(log10(enet_fit_B$bestTune$lambda) - 1,
                  log10(enet_fit_B$bestTune$lambda) + 1, length.out = 50)
)

enet_fine_B <- train(x_mat_B, y_vec_B,
                     method = "glmnet",
                     trControl = ctrl,
                     tuneGrid = fine_grid_B)

best_alpha_B <- enet_fine_B$bestTune$alpha
best_lambda_B <- enet_fine_B$bestTune$lambda
cat("Best alpha:", best_alpha_B, "\n")
cat("Best lambda:", best_lambda_B, "\n")
cat("CV RMSE:", min(enet_fine_B$results$RMSE, na.rm = TRUE), "\n")
cat("CV R-squared:", max(enet_fine_B$results$Rsquared, na.rm = TRUE), "\n")
```

```{r ols-refit-B}
enet_coefs_B <- coef(enet_fine_B$finalModel, s = best_lambda_B)
selected_B <- rownames(enet_coefs_B)[which(enet_coefs_B != 0)][-1]

refit_vars_B <- c()
for (v in all_predictors) {
  if (any(grepl(paste0("^", v), selected_B))) {
    refit_vars_B <- c(refit_vars_B, v)
  }
}
refit_vars_B <- unique(refit_vars_B)

refit_formula_B <- as.formula(
  paste("log_PFS ~", paste(refit_vars_B, collapse = " + "))
)
final_model_B <- lm(refit_formula_B, data = dat_b_model)
summary(final_model_B)
```

## Coefficient Comparison

```{r coef-compare, fig.width=8, fig.height=6, fig.cap="Coefficient comparison between Model A and Model B"}
coef_A <- as.data.frame(summary(final_model_A)$coefficients) |>
  mutate(Variable = rownames(summary(final_model_A)$coefficients),
         Model = "A (1990-1995)")

coef_B <- as.data.frame(summary(final_model_B)$coefficients) |>
  mutate(Variable = rownames(summary(final_model_B)$coefficients),
         Model = "B (2000-2005)")

coef_both <- bind_rows(coef_A, coef_B) |>
  filter(Variable != "(Intercept)")

ggplot(coef_both, aes(x = reorder(Variable, Estimate), y = Estimate,
                      color = Model)) +
  geom_point(position = position_dodge(width = 0.5), size = 2.5) +
  geom_errorbar(aes(ymin = Estimate - 1.96 * `Std. Error`,
                    ymax = Estimate + 1.96 * `Std. Error`),
                position = position_dodge(width = 0.5), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  coord_flip() +
  labs(title = "Coefficient Comparison: Model A vs Model B",
       x = NULL, y = "Estimate (95% CI)") +
  theme_bw()
ggsave("figures/coef_comparison.png", width = 8, height = 6, dpi = 300)
```

```{r coef-table-compare}
coef_wide <- coef_both |>
  select(Variable, Model, Estimate, `Pr(>|t|)`) |>
  pivot_wider(names_from = Model,
              values_from = c(Estimate, `Pr(>|t|)`),
              names_glue = "{Model}_{.value}")

kable(coef_wide, digits = 4,
      caption = "Table 5: Side-by-Side Coefficient Comparison") |>
  kable_styling(full_width = FALSE)
```

## Final Performance Summary

```{r final-summary}
pred_B_new <- predict(final_model_B, newdata = dat_b_model)

final_perf <- data.frame(
  Scenario = c("Model A on Data A",
               "Model A on Data B",
               "Model B on Data B"),
  R_squared = round(c(
    summary(final_model_A)$r.squared,
    R2_B,
    summary(final_model_B)$r.squared
  ), 4),
  RMSE = round(c(
    sqrt(mean((y_a - pred_A)^2)),
    RMSE_B,
    sqrt(mean((y_b - pred_B_new)^2))
  ), 4),
  MAE = round(c(
    mean(abs(y_a - pred_A)),
    MAE_B,
    mean(abs(y_b - pred_B_new))
  ), 4)
)

kable(final_perf,
      caption = "Table 6: Final Performance Summary Across All Scenarios") |>
  kable_styling(full_width = FALSE)
```
